\documentclass{amsproc}

\usepackage{hyperref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{xca}[theorem]{Exercise}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\numberwithin{equation}{section}

\begin{document}

\title{AQFT in Lean}

\author{Kelly J Davis}
\email{kdavis@alum.mit.edu}

\subjclass[2010]{Primary }

\keywords{AQFT}

\date{June 5, 2026}


\input{sections/sec0/abstract}
\maketitle
\pagebreak

\tableofcontents
\pagebreak

\section{Original Haag Kastler Axioms}\label{sec:original-haag-kastler-axioms}
\input{sections/sec1/original_haag_kastler_axioms}
\vfill
\pagebreak

\section{Axiom 0 (Minkowski Space)}\label{sec:axiom-0-(minkowski-space)}
``Minkowski space'' is referred to, directly or indirectly, in most of these axioms. However, a crisp, mathematical definition of ``Minkowski space'' is never given in Haag and Kastler's \href{https://doi.org/10.1063/1.1704187}{original work}. So, to clarify the axioms, we should provide one.

Normally this level of pedanticism isn't warranted. But, for example, Axiom 1 (Local Algebras) refers to the $\mathbf{B}$ as \textit{``open sets with compact closure in Minkowski space''}. So, the topology of ``Minkowski space'' \textit{is} relevant, and not all topologies may yield ``physical'' results.

All that being said, to ensure that the axioms are built on a solid foundation, we need a formal definition of ``Minkowski space'' to build them on.
\input{sections/sec2/2-1_standard_topology_on_minkowski_space}
\input{sections/sec2/2-2_indiscrete_topology_on_minkowski_space}
\input{sections/sec2/2-3_euclidean_topology_on_minkowski_space}
\input{sections/sec2/2-4_alexandrov_topology_on_minkowski_space}
\vfill
\pagebreak

\section{Axiom 1 (Local Algebras)}\label{sec:axiom-1-(local-algebras)}
Next let us consider Axiom 1 (Local Algebras) which states
 
\textbf{Axiom 1} \textit{(Local Algebras)} The ``regions'' $\mathbf{B}$ for which the correspondence

\begin{align}
\mathbf{B} \rightarrow \mathfrak{U}(\mathbf{B})
\end{align}

is defined shall be the open sets with compact closure in Minkowski space, the algebras $\mathfrak{U}(\mathbf{B})$ shall be (abstract) C\*-algebras.
\input{sections/sec3/3-1_regions_of_measurement}
\vfill
\pagebreak

\section{Axiom 2 (Isotony)}\label{sec:axiom-2-(isotony)}
Now let us consider Axiom 2 (Isotony) which states

\textbf{Axiom 2} \textit{(Isotony)} If $\mathbf{B_1} \subset \mathbf{B_2}$ then $\mathfrak{U}(\mathbf{B_1}) \subset \mathfrak{U}(\mathbf{B_2})$. We assume in addition that one of the two following situations prevails. Either $\mathfrak{U}(\mathbf{B_1})$ and $\mathfrak{U}(\mathbf{B_2})$ have a common unit element, or neither of them has a unit. The first situation can be obtained from the second by formal adjunction of a unit.
%\input{sections/sec3/3-1_regions_of_measurement}
\vfill
\pagebreak

\section{Axiom 3 (Local Commutativity)}\label{sec:axiom-3-(local-commutativity)}

\section{Axiom 4 (Quasilocal Algebra)}\label{sec:axiom-4-(quasilocal-algebra)}

\section{Axiom 5 (Lorentz Covariance)}\label{sec:axiom-5-(lorentz-covariance)}

\section{Axioms 6 (Primitivity)}\label{sec:axiom-6-(primitivity)}

\section{Haag Kastler Axioms Unpacked}\label{sec:haag-kastler-axioms-unpacked}

\end{document}
