\textbf{Axiom 1} \textit{(Local Algebras)} The ``regions'' $\mathbf{B}$ for which the correspondence
\begin{align}
\mathbf{B} \rightarrow \mathfrak{U}(\mathbf{B})
\end{align}
is defined shall be the open sets with compact closure in Minkowski space, the algebras $\mathfrak{U}(\mathbf{B})$ shall be (abstract) C\*-algebras.

\textbf{Axiom 2} \textit{(Isotony)} If $\mathbf{B_1} \subset \mathbf{B_2}$ then $\mathfrak{U}(\mathbf{B_1}) \subset \mathfrak{U}(\mathbf{B_2})$. We assume in addition that one of the two following situations prevails. Either $\mathfrak{U}(\mathbf{B_1})$ and $\mathfrak{U}(\mathbf{B_2})$ have a common unit element, or neither of them has a unit. The first situation can be obtained from the second by formal adjunction of a unit.

\textbf{Axiom 3} \textit{(Local Commutativity)} If $\mathbf{B_1}$ and $\mathbf{B_2}$ are completely spacelike with respect to each other, then $\mathfrak{U}(\mathbf{B_1})$ and $\mathfrak{U}(\mathbf{B_2})$ commute.

\textbf{Axiom 4} \textit{(Quasilocal Algebra)} The set-theoretic union of all $\mathfrak{U}(\mathbf{B})$ is a normed \*-algebra. Taking its completion we get a C\*-algebra which we denote by $\mathfrak{U}$ and call the \textit{algebra of quasilocal observables}. We maintain that $\mathfrak{U}$ contains all observables of interest.

\textbf{Axiom 5} \textit{(Lorentz Covariance)} The inhomogeneous Lorentz group is represented by automorphisms $A \in \mathfrak{U} \rightarrow A^L \in \mathfrak{U}$ such that
\begin{align}
\mathfrak{U}(\mathbf{B})^L = \mathfrak{U}(\mathbf{LB})
\end{align}
where $L\mathbf{B}$ is the image of the region $\mathbf{B}$ under the Lorentz transformation $L$.

\textbf{Axiom 6} \textit{(Primitivity)} $\mathfrak{U}$ is primitive.
